\huge A Usability Evaluation of Tor Launcher

### 2016-10-24 pets2017-paper/pets2017-paper.tex
hash out inspection section

\subsection{Procedure} 
{\color {blue}
David and I sat down in the same room, started from the first screen, and tried to toggle every single path in a systematic way, usually going with the default option first if any, then working from top to bottom.
}

\subsection{Observations}
{\color {blue}
Quick refer to the digraph, and explain everything in the caption. Put end states in the appendix (if it doesn't fit in the caption.

A short paragraph with 1-3 observations--using a non-leading tone! 
}

@@

\appendix
\section{Alternative Approaches} 
\label{alternatives}
{\color {blue}
Our goal was to deploy impactful, tested changes the Tor configuration interface. In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface. Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away. For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed. However, we list some alternative approaches that seem worth exploring. \\

>>>>

\subsection{Procedure} 
{\color {blue}
David and I (1 security/tor person and 1 usable security researcher) sat down in the same room, started from the first screen, and tried to toggle every single path in a systematic way, usually going with the default option first if any, then working from top to bottom. Along the way, we discussed when a certain option would need to be used, if the option seemed visible or helpful, and other things like that. 
}

\subsection{Observations}
{\color {blue}
Quick refer to the digraph, and explain everything in the caption. Put end states in the appendix (if it doesn't fit in the caption.  Appendix ~\ref{states}, Figure~\ref{fig:digraph}.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{tor-digraph.png}
\caption{
caption here. give example of e12,s2,e12',s2' refer to appendix for the list of all errors. 
% e12; selected proxy type, good address syntax, good ip address, blank port (bridge) 
% s2; selected proxy type, good address syntax, good ip address, blank port (bridge)
% e12'; selected proxy type, good address syntax, good ip address, blank port (no bridge)
% s2'; selected proxy type, good address syntax, good ip address, blank port (no bridge) 
}
\label{fig:digraph}
\end{figure*}

A short paragraph with 1-3 observations--using a non-leading tone! 1) most of this is only for the censorship use case 2) this assumed a level of technical familiarity in the user 3) lots of places where users can mess up--just look at the number of end states. 
}

@@

\appendix

\section{Success and Error States in Tor Launcher 5.0.3} 
\label{states} 
{\color {blue} 
success states: 
\begin{itemize}
\item s0: no bridge no proxy connection.
\item s1: bridge, no proxy connection.
\item s2: bridge and proxy connection (correct proxy syntax and with default port)
\item s3: bridge and proxy connection (correct proxy syntax and with specified port)
\end{itemize}

error states:
\begin{itemize} 
\item e0: custom bridge: field left blank
\item e1: custom bridge: syntax error
\item e2: custom bridge: good syntax, bad ip address
\item e3: hardcoded bridge: bridge blocked in country
\item e4: bridge blocked in country
\item e5: blank proxy input
\item e6: no proxy type
\item e7: selected proxy type, bad address syntax
\item e8: selected proxy type, good address syntax, bad ip address, blank port
\item e9: selected proxy type, good address syntax, bad ip address, good port
\item e10: selected proxy type, good address syntax, bad ip address, bad port
\item e11: selected proxy type, good address syntax, good ip address, bad port
\item e12: selected proxy type, good address syntax, good ip address, blank port
\end{itemize} 
}

\section{Alternative Approaches} 
\label{alternatives}
{\color {blue}
Our goal was to deploy impactful, tested changes the Tor configuration interface. In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface. Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away. For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed. However, we list some alternative approaches that seem worth exploring. \\
